Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

In this section,
we exercise the proposed framework through two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded,
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help achieving balance between energy consumption and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments have been released with a permissive open-source license and have been archived for future reference on
Zenodo~\cite{https://doi.org/10.5281/zenodo.7933160, https://doi.org/10.5281/zenodo.7948801}.

>>>>

In this section,
we exercise the proposed framework through two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for an urban event
and show how the dynamic reconfiguration may help to balance
cost, energy consumption and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments have been released with a permissive open-source license and have been archived for future reference on
Zenodo~\cite{https://doi.org/10.5281/zenodo.7933160, https://doi.org/10.5281/zenodo.7948801}.
